The Astropy Project

### 2017-11-21 main.tex
fix typo

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropkg 
provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst} 
over the course of the entire project and more details about individual 
subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.  
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

>>>>

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
provides a full log of changes \footnote{https://github.com/astropy/astropy/blob/master/CHANGES.rst}
over the course of the entire project and more details about individual
subpackages are available in the documentation \footnote{http://docs.astropy.org/en/stable/}.
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.
